Blocking-resistant communication\\through domain fronting

### 2015-02-09 docs/fronting.tex
\hyphenation{Go-Agent}
It was being broken as
	GoA-
	gent
CDN survey table.

\documentclass{sig-alternate}
\usepackage{txfonts}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xspace}
\usepackage{color}

\hyphenation{Client-Hello}

@@

@@

\vp{This whole section should be beefed up with a deeper assessment.  Along
these lines, it would help to include a summary table.}
This section contains a brief survey of fronting-capable
web services we have found, each with its pros and cons.
The list is not exhaustive and is meant to illustrate the broad
support for fronting that exists.
Of the services listed, we have so far deployed \meek
only on Google App Engine and Amazon CloudFront.
For the others, we have only checked that fronting works.
Recall that even web services that support fronting
will front only for their own customers,
so new each deployment typically requires an investment of time and money.

>>>>

\documentclass{sig-alternate}
\usepackage{txfonts}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xspace}
\usepackage{color}
\usepackage{threeparttable}

\hyphenation{Client-Hello Go-Agent}

@@

\newcommand{\yes}\checkmark

@@

\begin{table*}[ht]
\centering
\begin{threeparttable}

\caption{
Summary of fronting-capable services.
}
\label{tab:survey}

\begin{tabular}{l r r r r c}
service                    &        \$/GB & \$/10K requests & \$/hour & \$/month & allows SNI$\ne$Host\tnote{1} \\
\hline
Google App Engine\tnote{2} &        0.120 &              -- &    0.05 &       -- & \yes \\
Amazon CloudFront          & 0.085--0.250 &    0.010--0.022 &      -- &       -- & \yes \\
Microsoft Azure            & 0.087--0.138 &              -- &      -- &       -- & \yes \\
CloudFlare                 &           -- &              -- &      -- &      200 & \yes \\
Akamai\tnote{3}            &           -- &              -- &      -- &      400 & \yes \\
Fastly\tnote{4}            & 0.120--0.190 &    0.010--0.012 &      -- &       -- &      \\
Level~3\tnote{5}           & 0.035--0.200 &              -- &      -- &       -- & \\
% EdgeCast
\noalign{\smallskip}
\end{tabular}

\begin{tablenotes}
\item[1] A missing checkmark in the ``allows SNI$\ne$Host'' column means the service requires the ``domainless'' fronting style.
\item[2] App Engine dynamically scales the number of ``instances'' of the application code in order to handle changing load. Roughly, every instance after the first costs \$0.05/hour.
\item[3] Akamai does not publish pricing information; the prices here are from a reseller called Cache Simple, which quotes \$400/month for 1000~GB transfer, and \$0.50/GB beyond that.
\item[4] Fastly has a minimum montly charge of \$50.
\item[5] Level~3 does support domain fronting per se, but paths under the \urll{secure.footprint.net} domain can likely serve the same purpose. Level~3 does not publish pricing information; the prices here are from a reseller called VPS.NET, which quotes \$34.95 for the first 1000~GB and \$200 thereafter.
\end{tablenotes}

\end{threeparttable}
\end{table*}

In this section we survey a variety of web services and evaluate
their suitability for domain fronting.
Most of the services we evaluated support fronting in one form or another,
but they each have their own quirks and performance characteristics.
Table~\ref{tab:survey} summarizes the services.

This section contains a brief survey of fronting-capable
web services we have found, each with its pros and cons.
The list is not exhaustive and is meant to illustrate the broad
support for fronting that exists.
Of the services listed, we have so far deployed \meek
only on Google App Engine and Amazon CloudFront.
For the others, we have only checked that fronting works.
Recall that even web services that support fronting
will front only for their own customers,
so new each deployment typically requires an investment of time and money.
